SST_patterns

### 2019-11-19 SST_patterns.Rmd
update

# PLotting events

Loading the data
```{r}
load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")
load("Data/G1SST_upwell_base.RData")
```

@@

>>>>

Loading the data
    This is the data obtained once the upwelling signals were filtered out

```{r}
load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")
load("Data/G1SST_upwell_base.RData")
```

@@

# GLM - Determining if a change occur in the number of signals detected at different distancces from the coastline
